Reanalysis Step 3: Propensity Score Analysis with Twang

### 2025-08-30 reanalysis-2-multiple_imputation.qmd
ready to rerun final

@@

>>>>

  # Verify dr_severity was created properly
  if (!"dr_severity" %in% names(imp_data)) {
    stop("dr_severity not created in imputation ", i)
  }
  if (!is.factor(imp_data$dr_severity)) {
    stop("dr_severity is not a factor in imputation ", i)
  }

@@

### DR Severity Variable Check

```{r dr-severity-check}
# Verify dr_severity was created properly in all datasets
dr_severity_summary <- lapply(1:min(3, n_imputations), function(i) {
  imp_data <- imputed_datasets[[i]]

  # Check dr_severity exists and is a factor
  if (!"dr_severity" %in% names(imp_data)) {
    return(data.frame(imputation = i, status = "MISSING"))
  }

  # Get summary
  dr_table <- table(imp_data$dr_severity, useNA = "ifany")

  data.frame(
    imputation = i,
    No_DR = dr_table["No_DR"],
    NPDR = dr_table["NPDR"],
    PDR = dr_table["PDR"],
    Missing = sum(is.na(imp_data$dr_severity)),
    is_factor = is.factor(imp_data$dr_severity),
    n_levels = nlevels(imp_data$dr_severity)
  )
})

dr_summary_df <- do.call(rbind, dr_severity_summary)
kable(dr_summary_df, caption = "DR severity distribution in first 3 imputed datasets")

# Confirm factor levels are correct
if (is.factor(imputed_datasets[[1]]$dr_severity)) {
  cat("DR severity levels:", paste(levels(imputed_datasets[[1]]$dr_severity), collapse = ", "), "\n")
}
```

### 2025-08-30 reanalysis-4-propensity_scores.qmd
ready to rerun final

```{r ps-formula}
# Use original formula from get_matching_formula() 
# to maintain consistency with original analysis

ps_formula_original <- get_matching_formula()

@@

**Propensity score formula (original, without DR severity):**
```{r print-formula}
# Show the formula being used
print(ps_formula_original)

# Set the formula to use for analysis
ps_formula <- ps_formula_original
```

>>>>

```{r ps-formula}
# Use reanalysis formula that includes DR severity
# This is more comprehensive than the original formula

ps_formula_original <- get_matching_formula()
ps_formula_reanalysis <- get_matching_formula_reanalysis()

@@

**Original propensity score formula (without DR severity):**
```{r print-formula-original}
print(ps_formula_original)
```

**Reanalysis propensity score formula (with DR severity):**
```{r print-formula-reanalysis}
print(ps_formula_reanalysis)

# Use the reanalysis formula that includes dr_severity
ps_formula <- ps_formula_reanalysis
cat("\nUsing reanalysis formula with dr_severity for propensity score estimation.\n")
```
